UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-06-12 ms/main.tex
tweaks

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\columnwidth}
    \includegraphics[width=\columnwidth]{images/HRS_1000G_NP1_UMAP_PC7_NC2_NN15_MD05_pca_hrshisp_added1kgp_2018115153245_1kgp_hisp.pdf}
    \caption{}
    \label{fig:supp_umap_hrs_hisp_1kgp_hisp}
    \end{subfigure}\hfill
        \begin{subfigure}{0.5\columnwidth}
    \includegraphics[width=\columnwidth]{images/Asthma_FullAsian_PC_QC_new_UMAP_PC8_NC2_NN15_MD05_20193117303txt_eth_for_ms_lw2.jpeg}
    \caption{}
        \label{fig:umap_ukbb_indian}
    \end{subfigure}
    \caption{\textbf{Applying UMAP to subets of data can reveal deep population structure.} \textbf{(a)} UMAP on the top $7$ principal components of the self-identified Hispanic population of the HRS reveals a cluster (highlighted). Colouring the points by birthplace shows they were born almost entirely in the Mountain region (in green) of the United States (New Mexico, Arizona, Colorado, Utah, Nevada, Wyoming, Idaho, and Montana). When populations from the 1KGP are projected onto the UMAP embedding they do not map to the cluster. Six 1KGP populations are presented:
    CLM, Colombian in Medellin, Colombia;
    IBS, Iberian in Spain;
    MXL, Mexican in Los Angeles, California;
    PEL, Peruvian;
    PUR, Puerto Rican;
    TSI, Tuscani in Italy. Figure~\ref{fig:supp_umap_hrs_hisp_admix} presents the same projection of individuals from the HRS coloured by estimated admixture proportions. \textbf{(b)} UMAP on the top $8$ principal components of the self-identified Asian populations of the UKBB create clusters. Almost all individuals in the highlighted cluster are Indian individuals born in Kenya. Colours represent self-identified ethnic background, with those identifying as Indian coloured purple. }
    \label{fig:subpops}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{images/HRS_1000G_NP1_UMAP_PC7_NC2_NN15_MD05_pca_hrshisp_added1kgp_2018115153245_1kgp_hisp.pdf}
    \caption{}
    \label{fig:supp_umap_hrs_hisp_1kgp_hisp}
    \end{subfigure}\hfill
    \unskip\ \vrule\
        \begin{subfigure}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{images/Asthma_FullAsian_PC_QC_new_UMAP_PC8_NC2_NN15_MD05_20193117303txt_eth_for_ms_lw2.jpeg}
    \caption{}
        \label{fig:umap_ukbb_indian}
    \end{subfigure}
    \caption{\textbf{Applying UMAP to subsets of data can reveal deep population structure.} \textbf{(a)} UMAP on the top $7$ principal components of the self-identified Hispanic population of the HRS reveals a cluster (highlighted). Colouring the points by birthplace shows they were born almost entirely in the Mountain region (in green) of the United States (New Mexico, Arizona, Colorado, Utah, Nevada, Wyoming, Idaho, and Montana). When populations from the 1KGP are projected onto the UMAP embedding they do not map to the cluster. Six 1KGP populations are presented:
    CLM, Colombian in Medellin, Colombia;
    IBS, Iberian in Spain;
    MXL, Mexican in Los Angeles, California;
    PEL, Peruvian;
    PUR, Puerto Rican;
    TSI, Tuscani in Italy. Figure~\ref{fig:supp_umap_hrs_hisp_admix} presents the same projection of individuals from the HRS coloured by estimated admixture proportions. \textbf{(b)} UMAP on the top $8$ principal components of the self-identified Asian populations of the UKBB create clusters. Almost all individuals in the highlighted cluster are Indian individuals born in Kenya. Colours represent self-identified ethnic background, with those identifying as Indian coloured purple. }
    \label{fig:subpops}
\end{figure*}
